---
title: "cohort"
format: html
---

```{r}
library(arrow)
library(bigrquery)
library(dbplyr)
library(DBI)
library(gt)
library(gtsummary)
library(tidyverse)
library(forcats)
library(pryr)
library(data.table)
library(comorbidity)
library(tidymodels)
library(vip)
library(duckdb)
library(probably)
library(doParallel)
library(parallel)
```
```{r}
registerDoParallel(cores = parallel::detectCores() - 1)
```


```{r}
# path to the service account token 
satoken <- "biostat-203b-2026-winter-92fefbfab477.json"
# BigQuery authentication using service account
bq_auth(path = "~/BIOSTAT203B/203b-hw/hw4/biostat-203b-2026-winter-92fefbfab477.json")
```
Connect to BigQuery database `mimiciv_3_1` in GCP (Google Cloud Platform), using the project billing account `biostat-203b-2025-winter`.
```{r}
# connect to the BigQuery database `biostat-203b-2025-mimiciv_3_1`
con_bq <- dbConnect(
    bigrquery::bigquery(),
    project = "biostat-203b-2025-winter",
    dataset = "mimiciv_3_1",
    billing = "biostat-203b-2025-winter"
)
con_bq
```

Building the cohort: Joining transfers and icustays together
```{r}
# find all units listed under icustays
icu_careunits <- tbl(con_bq, "icustays") %>%
  distinct(first_careunit) %>%
  pull(first_careunit)
```

```{r}
# all transfers of patients who go from ed to icu per visit
ed_to_icu <- tbl(con_bq, "transfers") %>% #start with transfers
  mutate(
    is_ed = careunit == "Emergency Department",
    is_icu = careunit %in% icu_careunits
  ) %>%
  group_by(subject_id, hadm_id) %>%
  window_order(intime) %>%
  mutate( 
    is_last_ed = is_ed & !sql("LEAD(is_ed, 1, FALSE) OVER (
                      PARTITION BY subject_id, hadm_id
                      ORDER BY intime
                     )"),
    next_is_icu = sql("LEAD(is_icu, 1, FALSE) OVER (
                      PARTITION BY subject_id, hadm_id
                      ORDER BY intime     
                     )")
  ) %>%
  mutate(
    any_next_icu = sql("MAX(next_is_icu) OVER (
                      PARTITION BY subject_id, hadm_id
                      ORDER BY intime
                      ROWS BETWEEN CURRENT ROW AND UNBOUNDED FOLLOWING
                     )") 
  ) %>%
  ungroup() %>%
  filter(is_ed) %>%
  group_by(subject_id, hadm_id) %>%
  mutate( #can't use slice_min so we use row_number to get the first ed transfer per visit
    stay_num = sql("ROW_NUMBER() OVER (
                      PARTITION BY subject_id, hadm_id
                      ORDER BY intime
                     )")
  ) %>%
  filter(stay_num == 1) %>%
  ungroup() %>%
  left_join(
    tbl(con_bq, "icustays") %>%
      arrange(subject_id, hadm_id, intime) %>%
      group_by(subject_id, hadm_id) %>%
      filter(intime == min(intime)) %>%
      ungroup() %>%
      rename(intime_icu = intime, outtime_icu = outtime),
    by = c("subject_id", "hadm_id")
  ) %>%  # join in BQ
  select(-eventtype, -stay_num, -is_icu, 
         -last_careunit, -los, -transfer_id) %>%
  collect()

```

```{r}
ed_to_icu <- ed_to_icu %>%
  mutate(
    icu_within_3hrs = if_else(
      !is.na(intime_icu) & !is.na(intime) &
      intime_icu >= intime &
      intime_icu <= intime + hours(3),
      1L, 0L),
  ed_to_icu_minutes = if_else(
      !is.na(intime_icu) & !is.na(intime),
      as.numeric(difftime(intime_icu, intime, units = "mins")),
      NA_real_
    )
  )
ed_to_icu

```

```{r}
# # in ed_to_icu, but not ed_icu_basecase - 0
# anti_join(ed_to_icu, ed_to_icu_basecase, by = "hadm_id")
# 
# #in ed_to_icu_basecase but not ed_to_icu -
# anti_join(ed_to_icu_basecase, ed_to_icu, by = "hadm_id")
# 
# # in both
# semi_join(ed_to_icu, ed_to_icu_basecase, by = "hadm_id")
# 
# ed_to_icu %>%
#   group_by(hadm_id) %>%
#   summarize(n = n()) %>%
#   filter(n > 1)

sum(ed_to_icu$icu_within_3hrs == 1)
sum(!is.na(ed_to_icu$intime_icu))
```

Finding all trauma patients through ICD codes
```{r}
all_trauma_patients <- tbl(con_bq, "diagnoses_icd") %>%
    filter(
      # ICD-10 Logic: Must be version 10 AND within the S00-T88 range
      (icd_version == 10 & icd_code >= "S00" & icd_code <= "T88") | 
        
        # ICD-9 Logic: Must be version 9 AND (Numeric range OR E-code range)
        (icd_version == 9 & (
          (icd_code >= "800" & icd_code <= "959") | 
            (icd_code >= "E800" & icd_code <= "E999")
        ))
  ) %>%
  left_join(
    tbl(con_bq, "d_icd_diagnoses"),
    by = c("icd_code", "icd_version")
  ) %>%
  collect()
```

```{r}
ed_to_icu_trauma <- ed_to_icu %>%
  semi_join(
    all_trauma_patients,
    by = c("subject_id", "hadm_id")
  )

# number of stays that transferred within 3 hours
sum(ed_to_icu_trauma$icu_within_3hrs == 1)
# number of stays that did not go to the icu
sum(!is.na(ed_to_icu_trauma$intime_icu))

```

Now that we have all the patients and their stays, add in labs, vitals, and demographic data
```{r}
demographics <- tbl(con_bq, "patients") %>%
  select(subject_id, gender, anchor_age, anchor_year) %>%
  inner_join(
    tbl(con_bq, "admissions") %>%
      select(subject_id, hadm_id, insurance, 
             race, marital_status, admission_type),
    by = "subject_id") %>%
  collect()

ed_to_icu_trauma_demo <- ed_to_icu_trauma %>%
  inner_join(
    demographics,
    by = c("subject_id", "hadm_id")
  )

```
```{r}
lab_items_map <- c(
  "51222" = "hemoglobin",
  "51265" = "platelets",
  "50862" = "albumin",
  "50912" = "creatinine",
  "50971" = "potassium",
  "50983" = "sodium",
  "50902" = "chloride",
  "50882" = "bicarbonate",
  "51221" = "hematocrit",
  "51301" = "wbc",
  "50931" = "glucose",
  "50820" = "pH",
  "50818" = "pCO2",
  "50821" = "pO2",
  "50817" = "Oxygen Saturation",
  "50802" = "Base Excess",
  "50813" = "Lactate",
  "51006" = "Urea Nitrogen"
)

lab_item_ids <- as.integer(names(lab_items_map))

```

```{r}
labevents_tble <-
  open_dataset("labevents_pq", format = "parquet") %>%
  select(subject_id, hadm_id, itemid, charttime, valuenum) %>%
  filter(itemid %in% lab_item_ids,
         !is.na(charttime), 
         !is.na(valuenum)
  ) %>%
  mutate(
    subject_id = cast(subject_id, int32()),
    hadm_id = cast(hadm_id, int32()) ,
    charttime = cast(charttime, timestamp(unit = "us", timezone = "UTC"))
  )%>%
  inner_join(
    ed_to_icu_trauma_demo %>%
      select(subject_id, hadm_id, intime),
    by = c("subject_id", "hadm_id")
  ) %>%
  filter(!is.na(intime),
       charttime >= intime,
       charttime <= intime + dhours(3)
  ) %>%
  collect()

labs <- labevents_tble %>%
  group_by(subject_id, hadm_id, itemid) %>%
  slice_max(order_by = charttime, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  mutate(lab = recode(as.character(itemid), !!!lab_items_map)) %>%
  select(subject_id, hadm_id, lab, valuenum) %>%
  pivot_wider(names_from = lab, values_from = valuenum)

ed_to_icu_trauma_demo_labs <- ed_to_icu_trauma_demo %>%
  left_join(
    labs,
    by = c("subject_id", "hadm_id")
  )

```

Adding the vitals from the ED dataset
```{r}
vitals <- fread("~/BIOSTAT203B/mimic-iv-3.1/ed/vitalsign.csv.gz") %>%
  as_tibble()
edstays <- fread("~/BIOSTAT203B/mimic-iv-3.1/ed/edstays.csv.gz") %>%
  as_tibble()
```

```{r}
ed_vitals <- vitals %>%
  select(subject_id, stay_id, charttime, 
         temperature, heartrate, resprate, 
         o2sat, sbp, dbp) %>%
  inner_join(
    edstays %>% 
      select(subject_id, stay_id, hadm_id, intime, arrival_transport),
    by = c("subject_id", "stay_id")
  ) %>%
  filter(
     !is.na(intime),
     !is.na(charttime),
    charttime >= intime,
    charttime <= intime + hours(3)
  ) %>%
  pivot_longer(
    cols = c(temperature, heartrate, resprate, o2sat, sbp, dbp),
    names_to = "vital_name",
    values_to = "valuenum"
  ) %>%
  filter(!is.na(valuenum)) %>%
  group_by(subject_id, hadm_id, vital_name) %>%
  slice_max(order_by = charttime, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  pivot_wider(names_from = vital_name, values_from = valuenum) %>%
  collect() %>%
  select(-stay_id, -intime)

```

```{r}
ed_to_icu_trauma_demo_labs_vitals <- ed_to_icu_trauma_demo_labs %>%
  left_join(
    ed_vitals,
    by = c("subject_id", "hadm_id")
  )
rm(ed_to_icu_trauma_demo_labs)
rm(ed_vitals)
```

```{r}
ed_to_icu_trauma_demo_labs_vitals %>%
  group_by(icu_within_3hrs, next_is_icu) %>%
  count()

ed_to_icu_trauma_demo_labs_vitals %>%
  group_by(icu_within_3hrs) %>%
  count()

```

Adding Charlson score to account for comorbidities
```{r}
icd_visits <- tbl(con_bq, "diagnoses_icd") %>%
  inner_join(
    tbl(con_bq, "admissions") %>%
    group_by(subject_id) %>%
    arrange(admittime) %>%
    mutate(
      stay_seq = row_number()
    ) %>%
    select(subject_id, hadm_id, stay_seq, admittime, dischtime),
    by = c("subject_id", "hadm_id") 
  ) %>%
  collect()

```

```{r}
# get all the icd 9 codes that are needed for charlson score and see if a patient was diagnosed with them
map9 <- comorbidity(x = filter(icd_visits, icd_version == 9),
                    id = "hadm_id", code = "icd_code",
                    map = "charlson_icd9_quan", assign0 = TRUE)

# get all the icd 10 codes that are needed for charlson score and see if a patient was diagnosed with them
map10 <- comorbidity(x = filter(icd_visits, icd_version == 10),
                     id = "hadm_id", code = "icd_code",
                     map = "charlson_icd10_quan", assign0 = TRUE)

# put these maps together and join back into main dataset icd_visits
all_maps <- bind_rows(map9, map10) %>%
  group_by(hadm_id) %>%
  summarise(across(mi:aids, max)) %>%
  left_join(
    unique(select(icd_visits, subject_id, hadm_id, stay_seq)),
    by = "hadm_id"
  )

# make sure if previous stays have been diagnosed with certain code, future stays still have that recorded for patient history
final_cci <- all_maps %>%
  group_by(subject_id) %>%
  arrange(stay_seq) %>%
  mutate(across(mi:aids, ~ {
    # calculate cumulative history including current visit
    cum_history = cumany(.x == 1)
    # lag it by 1 so current visit only sees history from stay_seq - 1
    lag(cum_history, default = FALSE)
  })) %>%
  ungroup()

# for score to work, force meta tags to have class comorbidity and attributes to be charlson_icd10_quan
class(final_cci) <- c("comorbidity", class(final_cci))
attr(final_cci, "map") <- "charlson_icd10_quan"

# finally, weighted score based on all diagnoses
final_cci$charlson_score <- score( 
  final_cci, weights = "quan", assign0 = TRUE
)

```

```{r}
# only keep the stays where we are interested in the ed to icu transfers
ed_to_icu_trauma_demo_labs_vitals_charlson <- final_cci %>%
  select(subject_id, hadm_id, stay_seq, charlson_score) %>%
  right_join(
    ed_to_icu_trauma_demo_labs_vitals,
    by = c("subject_id", "hadm_id")
  )
rm(ed_to_icu_trauma_demo_labs_vitals)
rm(icd_visits)
rm(map9)
rm(map10)
rm(all_maps)
rm(final_cci)
```

```{r}
ed_to_icu_trauma_demo_labs_vitals_charlson %>%
  tbl_summary(by = icu_within_3hrs) %>%
  add_n(statistic = "{p_miss}")

```

Doing some feature engineering and pre-processing to get ready for modeling. Adding flags for whether each lab/vital was measured, and then dropping the original continuous lab/vital columns since we are only interested in whether they were measured or not for this project. Also adding some computed features like shock index and MAP, but only where both components are present, and an age variable that is anchored to the year of the visit instead of the current year.
```{r}
ed_to_icu_trauma_demo_labs_vitals_charl_flagged <- ed_to_icu_trauma_demo_labs_vitals_charlson %>%
  mutate(
    # vitals flags
    temperature_measured  = as.integer(!is.na(temperature)),
    heartrate_measured    = as.integer(!is.na(heartrate)),
    sbp_measured          = as.integer(!is.na(sbp)),
    dbp_measured          = as.integer(!is.na(dbp)),
    resprate_measured     = as.integer(!is.na(resprate)),
    o2sat_measured        = as.integer(!is.na(o2sat)),
    
    # lab flags
    lactate_measured      = as.integer(!is.na(Lactate)),
    hemoglobin_measured   = as.integer(!is.na(hemoglobin)),
    platelets_measured    = as.integer(!is.na(platelets)),
    wbc_measured          = as.integer(!is.na(wbc)),
    creatinine_measured   = as.integer(!is.na(creatinine)),
    sodium_measured       = as.integer(!is.na(sodium)),
    potassium_measured    = as.integer(!is.na(potassium)),
    bicarbonate_measured  = as.integer(!is.na(bicarbonate)),
    glucose_measured      = as.integer(!is.na(glucose)),
    bun_measured          = as.integer(!is.na("Urea Nitrogen")),
    ph_measured           = as.integer(!is.na(pH)),
    pco2_measured         = as.integer(!is.na(pCO2)),
    po2_measured          = as.integer(!is.na(pO2)),
    base_excess_measured  = as.integer(!is.na("Base Excess")),
    o2sat_measured        = as.integer(!is.na("Oxygen Saturation")),

    # computed features only where both components present
    shock_index           = if_else(!is.na(heartrate) & !is.na(sbp),
                                    heartrate / sbp, NA_real_),
    shock_index_measured  = as.integer(!is.na(shock_index)),
    map                   = if_else(!is.na(sbp) & !is.na(dbp),
                                    dbp + (1/3) * (sbp - dbp), NA_real_),
    map_measured          = as.integer(!is.na(map)),
    age_intime            = anchor_age + year(intime) - anchor_year,
    interdepartmental     = if_else(next_is_icu == FALSE & any_next_icu == TRUE, 1L, 0L),
    race = fct_collapse(race,
           ASIAN = str_subset(unique(race), "ASIAN"),
           BLACK = str_subset(unique(race), "BLACK"),
           HISPANIC = str_subset(unique(race), "HISPANIC"),
           WHITE = str_subset(unique(race), "WHITE"),
           other_level = "Other"),
    icu_within_3hrs = factor(icu_within_3hrs, 
                             levels = c(1, 0), 
                             labels = c("Yes", "No"))
  ) %>%
select(-careunit, -is_ed, -is_last_ed, -stay_id, -first_careunit,
       -intime_icu, -intime, -outtime_icu, outtime, -ed_to_icu_minutes,
       -anchor_year,
       -charttime, -"Oxygen Saturation", -next_is_icu, -any_next_icu,
       -intime, -outtime, -subject_id, -hadm_id)
  # drop all original continuous lab/vital columns

```


```{r}
final_cohort_flagged <- ed_to_icu_trauma_demo_labs_vitals_charl_flagged %>%
  select(-c(Lactate, hemoglobin, platelets, wbc, creatinine,
            sodium, potassium, bicarbonate, glucose, "Urea Nitrogen",
            pH, pCO2, pO2, "Base Excess", albumin, hematocrit,
            chloride, anchor_age))

```

```{r}
final_cohort_flagged %>%
  tbl_summary(by = icu_within_3hrs) %>%
  add_n(
    statistic = "{p_miss}"
  )
  
```

```{r}
#saveRDS(final_cohort_flagged, "final_cohort_flagged.rds")
```

### Modeling with Lasso Logistic Regression and Class Weights
# Adding Inverse Frequency Weights to address class imbalance and then doing the intial data split with a proportion of 0.75 for training and 0.25 for testing, stratified by the outcome variable `icu_within_3hrs`.
```{r}
set.seed(123)

n_total <- nrow(final_cohort_flagged)
n_no <- sum(final_cohort_flagged$icu_within_3hrs == "No")
n_yes <- sum(final_cohort_flagged$icu_within_3hrs == "Yes")


cohort_w1 <- final_cohort_flagged %>%
  mutate(class_weight = if_else(icu_within_3hrs == "Yes",
                        n_total / (2 * n_yes),
                        n_total / (2 * n_no)),
         class_weight = importance_weights(class_weight))

data_split_w1 <- initial_split(
  cohort_w1,
  strata = icu_within_3hrs,
  prop = 0.75
)

train_data_w1 <- training(data_split_w1)
test_data_w1 <- testing(data_split_w1)

levels(cohort_w1$icu_within_3hrs)
```

# Building the workflow recipe through preprocessing and model specification
```{r}
lassologit_recipe_w1 <-
  recipe(icu_within_3hrs ~ .,
         data = train_data_w1) %>%
  # mode imputation for insurance
  step_impute_mode(insurance) %>%
  # mode imputation for marital status
  step_impute_mode(marital_status) %>%
  # mode imputation for arrival_transport
  step_impute_mode(arrival_transport) %>%
  # median imputation for all vitals due to >50% & <65% missingness
  step_impute_median(temperature) %>%
  step_impute_median(heartrate) %>%
  step_impute_median(sbp) %>%
  step_impute_median(dbp) %>%
  step_impute_median(resprate) %>%
  step_impute_median(o2sat) %>%
  step_impute_median(map) %>%
  step_impute_median(shock_index) %>%
  # create traditional dummy variables
  step_dummy(all_nominal_predictors()) %>%
  # zero-variance filter
  step_nzv(all_predictors()) %>%
  # center and scale numeric features
  step_normalize(all_numeric_predictors())
```

```{r}
 lassologit_mod <-
   logistic_reg(
     penalty = tune(),
     mixture = 1
   ) %>%
   set_engine("glmnet", standardize = FALSE) %>%
   set_mode("classification")
```

```{r}
lassologit_wf_w1 <- workflow() %>%
  add_case_weights(class_weight) %>%
  add_model(lassologit_mod) %>%
  add_recipe(lassologit_recipe_w1) %>%
  print()
```

# Using cross validation to tune the penalty parameter for the lasso logistic regression model, using a grid of 50 values for the penalty parameter ranging from 10^-8 to 10^1 on the log scale. Evaluating model performance using AUC-ROC, AUC-PR, sensitivity, and specificity metrics.
```{r}
n_cores <- detectCores(logical = TRUE) - 1
cl <- makePSOCKcluster(n_cores)
registerDoParallel(cl)
cat("Running on", n_cores, "cores\n")

set.seed(123)
folds <- vfold_cv(train_data_w1, 
                  v = 10,
                  strata = icu_within_3hrs)

param_grid <- grid_regular(
  penalty(range = c(-8,1), trans = log10_trans()),
   levels = 50
  )

lassologit_fit_w1 <- lassologit_wf_w1 %>%
  tune_grid(
    resamples = folds,
    grid = param_grid,
    control = control_grid(save_pred = TRUE),
    metrics = metric_set(roc_auc, pr_auc, sensitivity, specificity)
  )

stopCluster(cl)
registerDoSEQ()
cat("Parallel cluster stopped\n")
```

```{r}
lassologit_fit_w1 %>%
  collect_metrics() %>%
  filter(.metric == "roc_auc") %>%
  ggplot(mapping = aes(x = penalty, y = mean)) +
  geom_point() +
  labs(x = "Penalty", y = "CV AUC") +
  scale_x_log10()
```

# Finding the best model after fitting the model to get the highest sensitivity, while maintaining at least 90% sensitivity, and then plotting the sensitivity and specificity across different classification thresholds to choose the optimal threshold for classifying a patient as being transferred to the ICU within 3 hours of ED presentation.
```{r}
lassologit_fit_w1 %>%
  show_best(metric = "roc_auc")
```

```{r}
best_lassologit_w1 <- lassologit_fit_w1 %>%
  select_best(metric = "roc_auc")
best_lassologit_w1
```

# After finding the best model based on the tuning results, we collect the predictions from the cross validation folds for that best model and then use the `threshold_perf()` function to calculate sensitivity and specificity across a range of classification thresholds from 0.05 to 0.7, and then plot these metrics across the thresholds to visually inspect where we can achieve at least 90% sensitivity while maximizing specificity.
```{r}
cv_preds <- lassologit_fit_w1 %>%
  collect_predictions(parameters = best_lassologit_w1)

threshold_data <- cv_preds %>%
  threshold_perf(truth = icu_within_3hrs, 
                 estimate = .pred_Yes,
                 thresholds = seq(0.05, 0.7, by = 0.01),
                 metrics = metric_set(sensitivity, specificity, j_index))

threshold_data %>%
  filter(.metric %in% c("sensitivity", "specificity")) %>%
  ggplot(aes(x = .threshold, y = .estimate, color = .metric)) +
    geom_line(linewidth = 1) +
    geom_hline(yintercept = 0.90, linetype = "dashed", color = "red") +
    labs(x = "Classification Threshold", 
         y = "Metric Estimate",
         title = "Sensitivity and Specificity Across Classification Thresholds",
         caption = "Dashed red line indicates 90% sensitivity") +
    theme_minimal()
```

```{r}
chosen_threshold <- threshold_data %>%
  filter(.metric == "sensitivity", .estimate >= 0.90) %>%
  slice_max(order_by = .threshold) %>%
  pull(.threshold)

cat("Chosen threshold:", chosen_threshold, "\n")
```

# Once threshold is chosen, we fit the best model on the whole dataset and evaluate its performance on the test set, and then we also look at the coefficients of the fitted model to see which features were most important in predicting whether a patient would be transferred to the ICU within 3 hours of ED presentation.
```{r}
final_lassologit_wf_w1 <- lassologit_wf_w1 %>%
  finalize_workflow(best_lassologit_w1)

final_lassologit_fit_w1 <- final_lassologit_wf_w1 %>%
  last_fit(split = data_split_w1,
           metrics = metric_set(roc_auc, pr_auc, sensitivity, specificity, precision, recall, f_meas))
```

```{r}
final_lassologit_fit_w1 %>%
  collect_metrics()
```

# Confusion Matrix
```{r}
preds <- final_lassologit_fit_w1 %>%
  collect_predictions() %>%
  mutate(.pred_class = if_else(.pred_Yes >= chosen_threshold, "Yes", "No"),
         .pred_class = factor(.pred_class, levels = c("Yes", "No")))

conf_mat(preds, truth = icu_within_3hrs, estimate = .pred_class)
```

```{r}
metric_set(sensitivity, specificity, precision, recall, f_meas)(
  preds, 
  truth = icu_within_3hrs, 
  estimate = .pred_class
  )
```

# Feature Importance
```{r}
# ── 12. Variable Importance ───────────────────────────────────────────────────
fit_parsnip_w1     <- extract_fit_parsnip(final_lassologit_fit_w1)
coefficients_df_w1 <- tidy(fit_parsnip_w1)
coefficients_df_w1

# Plot importance from tidy() — this uses the correct selected penalty
# vip() is NOT used here because it reads from the wrong lambda on the glmnet path
coefficients_df_w1 %>%
  filter(
    term != "(Intercept)",
    estimate != 0            # only features LASSO kept
  ) %>%
  mutate(
    term = reorder(term, abs(estimate)),
    direction = if_else(estimate > 0, "Positive", "Negative")
  ) %>%
  ggplot(aes(x = abs(estimate), y = term, fill = direction)) +
  geom_col() +
  scale_fill_manual(values = c("Positive" = "#2196F3", "Negative" = "#F44336")) +
  labs(
    title = "LASSO Feature Importance (Selected Penalty)",
    x = "Absolute Coefficient",
    y = NULL,
    fill = "Direction"
  ) +
  theme_minimal()
```


