---
title: "cohort"
format: html
---

```{r}
library(bigrquery)
library(dbplyr)
library(DBI)
library(gt)
library(gtsummary)
library(tidyverse)
library(forcats)
library(pryr)
library(data.table)
library(comorbidity)
```

```{r}
# path to the service account token 
satoken <- "biostat-203b-2026-winter-92fefbfab477.json"
# BigQuery authentication using service account
bq_auth(path = "~/BIOSTAT203B/203b-hw/hw4/biostat-203b-2026-winter-92fefbfab477.json")
```
Connect to BigQuery database `mimiciv_3_1` in GCP (Google Cloud Platform), using the project billing account `biostat-203b-2025-winter`.
```{r}
# connect to the BigQuery database `biostat-203b-2025-mimiciv_3_1`
con_bq <- dbConnect(
    bigrquery::bigquery(),
    project = "biostat-203b-2025-winter",
    dataset = "mimiciv_3_1",
    billing = "biostat-203b-2025-winter"
)
con_bq
```

Building the cohort: Joining transfers and icustays together
```{r}
# find all units listed under icustays
icu_careunits <- tbl(con_bq, "icustays") %>%
  distinct(first_careunit) %>%
  pull(first_careunit)
```

```{r}
# all transfers of patients who go from ed to icu per visit
ed_to_icu <- tbl(con_bq, "transfers") %>% #start with transfers
  mutate(
    is_ed = careunit == "Emergency Department",
    is_icu = careunit %in% icu_careunits
  ) %>%
  group_by(subject_id, hadm_id) %>%
  window_order(intime) %>%
  mutate( 
    is_last_ed = is_ed & !sql("LEAD(is_ed, 1, FALSE) OVER (
                      PARTITION BY subject_id, hadm_id
                      ORDER BY intime
                     )"),
    next_is_icu = sql("LEAD(is_icu, 1, FALSE) OVER (
                      PARTITION BY subject_id, hadm_id
                      ORDER BY intime     
                     )")
  ) %>%
  mutate(
    any_next_icu = sql("MAX(next_is_icu) OVER (
                      PARTITION BY subject_id, hadm_id
                      ORDER BY intime
                      ROWS BETWEEN CURRENT ROW AND UNBOUNDED FOLLOWING
                     )") 
  ) %>%
  ungroup() %>%
  filter(is_ed) %>%
  group_by(subject_id, hadm_id) %>%
  mutate( #can't use slice_min so we use row_number to get the first ed transfer per visit
    stay_num = sql("ROW_NUMBER() OVER (
                      PARTITION BY subject_id, hadm_id
                      ORDER BY intime
                     )")
  ) %>%
  filter(stay_num == 1) %>%
  ungroup() %>%
  left_join(
    tbl(con_bq, "icustays") %>%
      arrange(subject_id, hadm_id, intime) %>%
      group_by(subject_id, hadm_id) %>%
      filter(intime == min(intime)) %>%
      ungroup() %>%
      rename(intime_icu = intime, outtime_icu = outtime),
    by = c("subject_id", "hadm_id")
  ) %>%  # join in BQ
  select(-eventtype, -stay_num, -is_icu, 
         -last_careunit, -los, -transfer_id) %>%
  collect()

```
```{r}
ed_to_icu <- ed_to_icu %>%
  mutate(
    icu_within_3hrs = if_else(
      !is.na(intime_icu) & !is.na(intime) &
      intime_icu >= intime &
      intime_icu <= intime + hours(3),
      1L, 0L),
  ed_to_icu_minutes = if_else(
      !is.na(intime_icu) & !is.na(intime),
      as.numeric(difftime(intime_icu, intime, units = "mins")),
      NA_real_
    )
  )
ed_to_icu

```

```{r}
# # in ed_to_icu, but not ed_icu_basecase - 0
# anti_join(ed_to_icu, ed_to_icu_basecase, by = "hadm_id")
# 
# #in ed_to_icu_basecase but not ed_to_icu -
# anti_join(ed_to_icu_basecase, ed_to_icu, by = "hadm_id")
# 
# # in both
# semi_join(ed_to_icu, ed_to_icu_basecase, by = "hadm_id")
# 
# ed_to_icu %>%
#   group_by(hadm_id) %>%
#   summarize(n = n()) %>%
#   filter(n > 1)

sum(ed_to_icu$icu_within_3hrs == 1)
sum(!is.na(ed_to_icu$intime_icu))
```

Finding all trauma patients through ICD codes
```{r}
all_trauma_patients <- tbl(con_bq, "diagnoses_icd") %>%
    filter(
      # ICD-10 Logic: Must be version 10 AND within the S00-T88 range
      (icd_version == 10 & icd_code >= "S00" & icd_code <= "T88") | 
        
        # ICD-9 Logic: Must be version 9 AND (Numeric range OR E-code range)
        (icd_version == 9 & (
          (icd_code >= "800" & icd_code <= "959") | 
            (icd_code >= "E800" & icd_code <= "E999")
        ))
  ) %>%
  left_join(
    tbl(con_bq, "d_icd_diagnoses"),
    by = c("icd_code", "icd_version")
  ) %>%
  collect()
```

```{r}
ed_to_icu_trauma <- ed_to_icu %>%
  semi_join(
    all_trauma_patients,
    by = c("subject_id", "hadm_id")
  )

# number of stays that transferred within 3 hours
sum(ed_to_icu_trauma$icu_within_3hrs == 1)
# number of stays that did not go to the icu
sum(!is.na(ed_to_icu_trauma$intime_icu))
```

Now that we have all the patients and their stays, add in labs, vitals, and demographic data
```{r}
demographics <- tbl(con_bq, "patients") %>%
  select(subject_id, gender, anchor_age, anchor_year) %>%
  inner_join(
    tbl(con_bq, "admissions") %>%
      select(subject_id, hadm_id, insurance, 
             race, marital_status, admission_type),
    by = "subject_id") %>%
  collect()

ed_to_icu_trauma_demo <- ed_to_icu_trauma %>%
  inner_join(
    demographics,
    by = c("subject_id", "hadm_id")
  )
  
```
```{r}
lab_items_map <- c(
  "50811" = "hemoglobin",
  "51704" = "platelets",
  "50862" = "albumin",
  "50912" = "creatinine",
  "50971" = "potassium",
  "50983" = "sodium",
  "50902" = "chloride",
  "50882" = "bicarbonate",
  "51221" = "hematocrit",
  "51301" = "wbc",
  "50931" = "glucose",
  "50820" = "pH",
  "50818" = "pCO2",
  "50821" = "pO2",
  "50817" = "Oxygen Saturation",
  "50802" = "Base Excess",
  "52442" = "Lactate",
  "52647" = "Urea Nitrogen"
)

lab_item_ids <- as.integer(names(lab_items_map))
```

```{r}
labevents_tble <- tbl(con_bq, "labevents") %>%
  select(subject_id, hadm_id, itemid, charttime, valuenum) %>%
  filter(itemid %in% lab_item_ids,
         !is.na(charttime), 
         !is.na(valuenum)
         ) %>%
  collect()

```

```{r}
labs <- labevents_tble %>%
  filter(!is.na(charttime)) %>%
  inner_join(
    ed_to_icu_trauma_demo %>%
      select(subject_id, hadm_id, intime),
    by = c("subject_id", "hadm_id")
  ) %>%
  filter(!is.na(intime),
         charttime >= intime,
         charttime <= intime + hours(3)) %>%
  group_by(subject_id, hadm_id, itemid) %>%
  slice_max(order_by = charttime, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  mutate(lab = recode(as.character(itemid), !!!lab_items_map)) %>%
  select(subject_id, hadm_id, lab, valuenum) %>%
  pivot_wider(names_from = lab, values_from = valuenum)

ed_to_icu_trauma_demo_labs <- ed_to_icu_trauma_demo %>%
  left_join(
    labs,
    by = c("subject_id", "hadm_id")
  )
```

Adding the vitals from the ED dataset
```{r}
ed_vitals <- fread("~/BIOSTAT203B/mimic-iv-3.1/ed/vitalsign.csv.gz") %>%
  left_join(
    fread("~/BIOSTAT203B/mimic-iv-3.1/ed/edstays.csv.gz"),
    by = c("subject_id", "stay_id")
  ) %>%
  filter(!is.na(intime),
         charttime >= intime,
         charttime <= intime + hours(3)) %>%
  group_by(subject_id, hadm_id) %>%
  slice_max(order_by = charttime, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  select(-stay_id, -gender, -race, -disposition, -intime, -outtime, -rhythm)

```

```{r}
ed_to_icu_trauma_demo_labs_vitals <- ed_to_icu_trauma_demo_labs %>%
  left_join(
    ed_vitals,
    by = c("subject_id", "hadm_id")
  )
```

```{r}
ed_to_icu_trauma_demo_labs_vitals %>%
  group_by(icu_within_3hrs, next_is_icu) %>%
  count()

ed_to_icu_trauma_demo_labs_vitals %>%
  group_by(icu_within_3hrs) %>%
  count()

```

Adding Charlson score to account for comorbidities
```{r}
icd_visits <- tbl(con_bq, "diagnoses_icd") %>%
  inner_join(
    tbl(con_bq, "admissions") %>%
    group_by(subject_id) %>%
    arrange(admittime) %>%
    mutate(
      stay_seq = row_number()
    ) %>%
    select(subject_id, hadm_id, stay_seq, admittime, dischtime),
    by = c("subject_id", "hadm_id") 
  ) %>%
  collect()

```

```{r}
# get all the icd 9 codes that are needed for charlson score and see if a patient was diagnosed with them
map9 <- comorbidity(x = filter(icd_visits, icd_version == 9),
                    id = "hadm_id", code = "icd_code",
                    map = "charlson_icd9_quan", assign0 = TRUE)

# get all the icd 10 codes that are needed for charlson score and see if a patient was diagnosed with them
map10 <- comorbidity(x = filter(icd_visits, icd_version == 10),
                     id = "hadm_id", code = "icd_code",
                     map = "charlson_icd10_quan", assign0 = TRUE)

# put these maps together and join back into main dataset icd_visits
all_maps <- bind_rows(map9, map10) %>%
  group_by(hadm_id) %>%
  summarise(across(mi:aids, max)) %>%
  left_join(
    unique(select(icd_visits, subject_id, hadm_id, stay_seq)),
    by = "hadm_id"
  )

# make sure if previous stays have been diagnosed with certain code, future stays still have that recorded for patient history
final_cci <- all_maps %>%
  group_by(subject_id) %>%
  arrange(stay_seq) %>%
  mutate(across(mi:aids, ~ {
    # calculate cumulative history including current visit
    cum_history = cumany(.x == 1)
    # lag it by 1 so current visit only sees history from stay_seq - 1
    lag(cum_history, default = FALSE)
  })) %>%
  ungroup()

# for score to work, force meta tags to have class comorbidity and attributes to be charlson_icd10_quan
class(final_cci) <- c("comorbidity", class(final_cci))
attr(final_cci, "map") <- "charlson_icd10_quan"

# finally, weighted score based on all diagnoses
final_cci$charlson_score <- score( 
  final_cci, weights = "quan", assign0 = TRUE
)

```

```{r}
# only keep the stays where we are interested in the ed to icu transfers
ed_to_icu_trauma_demo_labs_vitals_charlson <- final_cci %>%
  select(subject_id, hadm_id, stay_seq, charlson_score) %>%
  right_join(
    ed_to_icu_trauma_demo_labs_vitals,
    by = c("subject_id", "hadm_id")
  )
```

```{r}
single <- ed_to_icu_trauma %>%
  filter((next_is_icu | any_next_icu) & is.na(stay_id)) %>%
  collect()

```

```{r}
icu_careunits
  
```








